\documentclass[12pt]{article}
\begin{document}
\title{ A REPORT ON WHY BUSINESSES NEEDS SOCIAL MEDIA.}


\maketitle
\author {KISEMBO Rhitah  14/U/8028/ps}

\section{Introduction}
According to the study undertaken, it is believed that social media used as a marketing platform plays a  big role in facilitating the growth of the business since it enables the marketing department to reach a large number of people within a limited period of time. This therefore calls for the adoption of the idea.
During the data collection process methods like the electric questionnaires were used and the instruments that aided the process were phones, laptops and the ODK collect application.

\section{ Problem Statement}
It is very hard or even impossible to make people aware of the company’s products or services delivered by using people alone to market the product. This is simply because they might not be able to do the assigned tasks as expected by word of mouth, however, by using social media applications or websites businesses are able to reach millions of people across the globe informing them of their products or services therefore facilitating growth.
\section{Aim and specific objectives}
\subsection{General objective}
The main aim of undertaking this research was;
To increase the customer base of the business through increased awareness of the products or services delivered hence increased business growth. Branding helps the customers easily recognise the business.
\section{Specific objectives}
The specific objectives of the study were as follows;
To develop an electronic data collection form that will be used to collect data.
To manage relationships with the customers since there is continued communication between the customers and the business owners.
To increase profits of the business by focusing more on the products that are highly demanded by the customers.
To help the business owner understand how people think of his or business directly.
\section{Research scope}
This study was carried out to investigate how social media is used to market goods and services thus facilitating increased business growth. The study was basically carried around the areas of Kampala as well as its suburbs.
\section{Methodology}
\subsection{Research questions }
The research questions to be answered are as follows:
What is the name of your business?
What is your position in the business?
What product(s) do you deal in?
Do you think social media is needed in business?
Give reason(s) why it is need or not?
Do you think social advertisement can improve business growth?
Do you think social decreases marketing costs?
Do you think social media is likely to attract more customers?
To what extent is it likely to do so?	
\subsection{Research Design }






\subsection{Instruments}
The Laptop
This enabled me to create the form that I later used to collect the data from various businesses as well as viewing the research results.
The mobile phone
This is where the ODK Collection Application was downloaded and installed from Google play store. It was used by the respondent to answer the questions and the information stored in the server.
\subsection{Data collection }
I had to move from one place to another to look for potential respondents. I collected the data using the program known ODK Collect Application that I had installed on the phone.  This had a set of questions I presented to the respondent where he or she had to fill the blank form by either typing the correct answer or checking a response according to their own understanding. The questions were in English and in cases where one couldn’t read or type I had to interpret the questions accordingly.

\subsection{Data Analysis }
Data was entered into the computer using ODK collect application that had been installed on the phone. Users or respondents filled blank forms and the information provided stored on the server for later analysis.
 The various ordinates stored were used to analyse the different data elements

\subsection{Limitations }
Some of the people weren’t ready to reveal their information for the purpose of security hence denying me the opportunity to come up with the necessary data.
Some of the potential responds were illiterate, they would read or type. This led to taking a lot of time on a single person since there was need for me to interpret the questions.
Recommendations
Businesses need to use social media as a marketing strategy to grow and expand at a faster rate because it increases the customer base


\end{document}
